---
title: "Class 5: Data Vis with ggplot"
author: "Jonathan Zau"
format: html
---

## `plot()` From The *base* Package in R

*cars* is a table of various cars' speed before braking, and their stopping distance.

```{r}
plot(cars)
```

## The Extremely Popular `ggplot2` Package

Don't forget to install ggplot2 before using it! Please input `install.packages("ggplot2)` into your local console.

```{r}
library("ggplot2")
ggplot(data = cars, mapping = aes(x = speed, y = dist))+
  geom_point()
```

Let's draw a best fit line.

```{r}
ggplot(data = cars, mapping = aes(x = speed, y = dist))+
  geom_point()+
  geom_smooth(se = FALSE)+
  labs(title = "Stopping Distance vs. Braking Speed",
       x = "Speed (mph)",
       y = "Distance (ft)"
       )+
  theme_bw()
```

`ggplot2` builds graphs in layers, so the order the computer reads your `ggplot()` function matters.

Almost all graphs using `ggplot2` has three layers:

1. **Data:** The numbers the computer uses to plot.
2. **Aesthetics:** Shortened to "aes", how the computer maps your data columns to the graph.
3. **Geometries:** Shortened to "geom", the type of graph your data will be plotted as, e.g. points, bars, etc.

Let's look at a more interesting data set, *mtcars*.

```{r}
ggplot(data = mtcars, mapping = aes(y = disp, x = mpg))+
  geom_point(aes(size = hp), color = "blue")+
  facet_wrap(~am)
```

## Conclusion

base `plot()` is good for making simple, quick graphs of your data, while `ggplot2` is good for making complex graphs.